---
title: "README"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This package gives you the option to talk like the main characters
of star trek The next generation. 

This package is proudly brought to you  by the RTrek community. 

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/startrek)](https://cran.r-project.org/package=startrek) [![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)


# How to use this package

call functions with the name of the characters
`Picard()` , `Geordi()`, etc

```{r}
library(startrek)
Picard()
Guinan()
```
## Installation
This package is not on cran. Nor should it be.
install with:
```{r eval=FALSE}
devtools::install_github("Rtrek/startrekpackage")
```

## Notes
I have filtered the spoken words of the main characters from the rest of the script.
If you would like all sentances in every episode spoken by 
everyone, you have to use the data from [here](https://github.com/RTrek/TNG "data only")

Code that created the dataset can be found [here](https://github.com/RTrek/startrekTNGdataset "contains code")

## Errors, help, great ideas or comments?
Did I make spelling errors or do you have an awesome idea?
Contact me by opening an issue on top of this page,
sending me a pull request (PR)
or emailing me. 

Kind regards,
Roel.
