---
title: "Use of this package"
author: "Roel M. Hogervorst"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

An R-package: the final frontier. These are the voyages of the R-package startrek. Its continuing mission: to explore strange new worlds, to seek out new life and new civilizations, to boldly go where no one has gone before. Or to give you a random phrase from one of the main characters in the TNG series.

You have the following options:

```{r options}
library(startrek)
Guinan()
Worf()
Wesley()
Picard()
Beverly()
Data()
Geordi()
Troi()
Pulaski()
Q()
Riker()
```

There are also other options
```{r other options}
Computer()
random_tng_character()
```


## Underlying technology

The package uses a state of the art data.frame that contains
all the phrases scraped from the original [episode scripts](https://github.com/RTrek/TNG "data only"). 

The code filters the dataframe on character and chooses
a random phrase. 
